The Impact of Subway Systems on Air Pollution

### 2023-02-26 output paper/Paper Two .qmd
replace

---
title: "The Impact of Subway Systems on Air Pollution"
author: 'Shaohan Chang and Ruibo Sun'
date: 02-20-2023
abstract: The investigation into how subway system openings affect urban air pollution, with a focus on particulate concentrations, is presented in this abstract. The study discovered that the opening of a subway system was associated with a 4% decrease in particulates in the area of the city center, which persisted over a four-year time horizon, in cities with higher initial pollution levels. In heavily polluted cities, this reduction was projected to have an annual external mortality benefit of about $1 billion. The findings imply that a significant portion of the cost of building subways may be offset by the reduced mortality caused by less air pollution. The results of this study can be repeated in other cities to learn more about the connection between air pollution and subway openings.
date-format: "MM/DD/YYYY" 
format: pdf
bibliography: "bib.bib"
---

# 1. Introduction

Air pollution is a significant contributor to the development of disease and premature death, and is widely recognized as the largest environmental risk factor to human health globally @a. Exposure to air pollution increases the risk of premature mortality from heart disease, stroke, and lung cancer. Advances in health and atmospheric sciences have made it possible to estimate the number of deaths and illnesses associated with air pollution, using information from peer-reviewed scientific literature. The relationship between population-level pollution exposure, both short-term and long-term, and adverse health outcomes, including premature death and hospital visits, is expressed through the concentration-response function. From @b, the Institute for Health Metrics and Evaluation and the Health Effects Institute, and the World Health Organization have developed estimates of air pollution-attributable deaths and other adverse health outcomes globally and for individual countries @c.

@@

\newpage
# Reference

>>>>

---
title: "The Impact of Subway Systems on Air Pollution"
author: 'Shaohan Chang and Ruibo Sun'
abstract: The investigation into how subway system openings affect urban air pollution, with a focus on particulate concentrations, is presented in this abstract. The study discovered that the opening of a subway system was associated with a 4% decrease in particulates in the area of the city center, which persisted over a four-year time horizon, in cities with higher initial pollution levels. In heavily polluted cities, this reduction was projected to have an annual external mortality benefit of about $1 billion. The findings imply that a significant portion of the cost of building subways may be offset by the reduced mortality caused by less air pollution. The results of this study can be repeated in other cities to learn more about the connection between air pollution and subway openings.
thanks: 'The code and the data are in https://github.com/ruibosun/paper2 .The replication of various aspects in this paper are available at  https://doi.org/10.3386/w24183' 
date: 02-20-2023
date-format: "MM/DD/YYYY"  
format: pdf
bibliography: "bib.bib"
---

# 1. Introduction
Air pollution is a significant contributor to the development of disease and premature death, and is widely recognized as the largest environmental risk factor to human health globally @a. Exposure to air pollution increases the risk of premature mortality from heart disease, stroke, and lung cancer. Advances in health and atmospheric sciences have made it possible to estimate the number of deaths and illnesses associated with air pollution, using information from peer-reviewed scientific literature. The relationship between population-level pollution exposure, both short-term and long-term, and adverse health outcomes, including premature death and hospital visits, is expressed through the concentration-response function. From @b, the Institute for Health Metrics and Evaluation and the Health Effects Institute, and the World Health Organization have developed estimates of air pollution-attributable deaths and other adverse health outcomes globally and for individual countries @c.

@@

# Claims identified by reproducer

1. Subway systems can reduce air pollution: The study found that opening subways in an average city could prevent infant deaths and total deaths per year, suggesting that subway systems may be cost-effective in reducing air pollution, especially in cities with high initial levels of aerosol optical depth (AOD).

2. No difference in traffic behavior between developed and developing cities: The study concluded that there are no differences in the way developed and developing cities react to subways, which is a significant finding for developing nations that may have a greater need for affordable air pollution solutions.

3. AOD is a reliable predictor of ground-measured particulate matter: The study used satellite imagery and remote sensing measurements of suspended particulate matter to evaluate the correlation between remotely sensed AOD and ground-based measurements of particulate matter (pm10 and pm2.5). The findings demonstrated that AOD is a highly reliable predictor of ground-measured particulate matter.

# Reference
